The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
update network methods

```
open <- c(1, 6, 7, 9)
forest <- c(2, 3, 4, 5)
lichen <- 8
```
### Generating multilayer social networks
We used R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION) to generate proximity-based social network layers from GPS telemetry data (see above). We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). We represented individuals in our networks by nodes and associations between individuals were represented by edges.

@@

Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer).

@@

Social networks constructed using spatsoc (Robitaille et al. 2019). Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.

>>>>

```
open <- c(1, 6, 7, 9)
forest <- c(2, 3, 4, 5)
lichen <- 8
```
### Caribou multilayer social networks

#### Network types and construction (defining layers for the multilayer network)

We generated seasonal multilayer social networks consisting of habitat-specific monolayers. Each layer was the social association network generated in one of three habitat types (lichen, open, and closed). Briefly, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION).

We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). We represented individuals in our networks by nodes and associations between individuals were represented by edges.

@@

@@

As above, we generated social association networks in three habitat types and two seasons. We generated separate multilayer networks consisting of  for each season. Variable modified is the spatial buffer. Series from 5 to 500.
